Methods and Results

### 2021-03-31 ms.Rmd
More results

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable)
  source("./R/func.R")
```
```{r loaddata, echo = FALSE, results = "hide"}
  # Tree
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)

@@

# Table 1: Effect, confidemce intervals, prediction intervals, heterogenity
            table1 <- make_table(model1.1, data)
      hetero_table <- I2(model1.1, v = data$v_SMDH)
hetero_table_phylo <- I2(model1.2, v = data$v_SMDH, phylo = "species2")

@@

  model1.3 <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
  robust(model1.3, cluster = data$study)

@@

  model1.5 <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
  robust(model1.5, cluster = data$study)

@@

```{r funnel, fig.height=4.5, fig.width=4.5, fig.cap="Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error). 95% pseudoconfidence intervals are provuded."}
funnel(model1.1, yaxis="seinv", digits = 2, las = 1)

@@

#### Female fitness is comproised more in species with male-biased sexual size dimorphism (SSD)

>>>>

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, ggarrange)
  source("./R/func.R")
```
```{r loaddata, echo = FALSE, results = "hide"}
  # Tree
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)

@@

# Table 1: Effect, confidemce intervals, prediction intervals, heterogenity
            table1 <- make_table(model1.1, data)
      hetero_table <- I2(model1.1, v = data$v_SMDH) # Same as orchaRd::i2_ml(model1.1)
hetero_table_phylo <- I2(model1.2, v = data$v_SMDH, phylo = "species2")

@@

  model1.3 <- rma.mv(SMDH ~ scale(SSD_lnRR), V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
  robust(model1.3, cluster = data$study)

  r2_SSD=r2_ml(model1.3)

@@

  r2_ml(model1.4)

  model1.5 <- rma.mv(SMDH ~ Harm_type + scale(SSD_lnRR), V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
  robust(model1.5, cluster = data$study)

@@

```{r funnel, fig.height=5, fig.width=16, fig.cap="A) Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error). B) orchaRd plot of the overall meta-analytic mean efect size, 95% confidnece intervals (thick black bars) and 95% prediction intervals (whiskers)"}
p1 <- ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDH), xmin = -6, xmax = 6)) +
geom_point(aes(colour = class)) +
labs(x = "SMDH", 
	 y = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
	 colour = "Class") +
scale_color_grey() + 
#scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9")) + 
theme_bw()

p2 <- orchard_plot(model1.1, mod = "Int", xlab = "SMDH") + scale_colour_manual(values = "grey") + scale_fill_manual(values = "red")

p1 + p2 + plot_annotation(tag_levels = c('A', 'B'))

@@

#### Female fitness is less compromised in species with reversed sexual size dimorphism (SSD)

Species where females are larger than males (i.e., negative SSD) are less impacted by sexual conflict compared to spcies where males and females are closer in size or males are larger (i.e., SSD > 0) (z-transformed $\beta_{SSD}$ = `r model1.3$beta[2]`, 95% CI = `r model1.3$ci.lb[2]` to `r model1.3$ci.ub[2]`, Figure \@ref(fig:SSD) , $R^2_{marginal}$ = `r r2_SSD[1]*100`% of effect size variation).

```{r SSD, fig.width=6, fig.height=4.5}
p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH))) + 
    geom_point() + 
      theme_bw() + 
  labs(x = "SSD", 
	     y = "SMDH",
	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
	guides(size = guide_legend(direction = "vertical"))

p3
```
